On the Design, Use and Removal of Eval in R

### 2020-08-10 inst/paper/main.tex
Reorganize as R package

\section{Related Work}
\eval has been widely discussed in the research literature for the challenges it
imposes for code comprehension and automated code analyses.
Perhaps, \citeit{EvalMenDo} is the most popular exposition of \eval and its
challenges for JavaScript.

>>>>

\section{Related Work}
eval has been widely discussed in the research literature for the challenges it
imposes for code comprehension and automated code analyses.
Perhaps, EvalMenDo is the most popular exposition of eval and its
challenges for JavaScript.
